\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

The proper validation of RDF data according to constraints is a common requirement of data practitioners. 
Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like \emph{DTD}, \emph{XML Schema}, \emph{RELAX NG}, or \emph{Schematron}.

@@

\begin{table}
	\centering
	  %\caption{Constraint Type Specific Expressivity}
		\caption{Constraint Type Specific Expressivity of Constraint Languages}
	  \scriptsize
		\begin{tabular}{c|c|c|c|c}
      %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & OWL 2 & \emph{SPIN} \\	
      \hline
			17.3 (14) & 25.9 (21) & 29.6 (24) & 67.9 (55) & \textbf{100.0} \textbf{(81)} 
		\end{tabular}
	\label{tab:constraint-type-specific-expressivity}
\end{table}

>>>>

The proper validation of RDF data according to constraints is a common requirement of data practitioners. 
Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like DTD, XML Schema, RELAX NG, or Schematron.

@@

\begin{table}[H]
	\centering
	  %\caption{Constraint Type Specific Expressivity}
		\caption{Constraint Type Specific Expressivity of Constraint Languages}
	  \scriptsize
		\begin{tabular}{c|c|c|c|c}
      %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & OWL 2 & \emph{SPIN} \\	
      \hline
			17.3 (14) & 25.9 (21) & 29.6 (24) & 67.9 (55) & \textbf{100.0} \textbf{(81)} 
		\end{tabular}
	\label{tab:constraint-type-specific-expressivity}
\end{table}
